Tracing the Hercules stream around the Galaxy

### 2010-09-09 tex/response.txt

	 1. On page 2, last paragraph of the introduction it is stated
	 that "propose and ... test of the bar resonance model for the
	 Hercules stream". However, this statement is not really
	 carried through in the text. It might be a good idea to
	 connect back to this statement in e.g. Sect 5 and tell the
	 reader how "testable" this model is once all the
	 uncertainties of data and shortcomings of the missions has
	 been discussed. The test and properties of the bar are also
	 mentioned in the abstract, however, there is no discussion in
	 the paper of how the properties of the bar are constrained by
	 the proposed observational test. Add this discussion, which
	 would be very interesting.

	 2. Page 2, statement at the end of the first paragraph "..up
	 to the task of separating out these effects." This statement
	 should be supported with a few relevant references.

	 3. On page 5, sect 4, third paragraph, last sentence. I do
	 not understand what the last sentence means - could the
	 author please re-phrase it? The sentence somehow, does not
	 connect to the previous text.

I thought this followed clearly from the sentences before it, but I
have changed this sentence to

Even though upcoming surveys such as APOGEE have the ability to probe
the other side of the Galaxy, for the purposes of detecting the
Hercules stream this is uninteresting as it does not show up in the
line-of-sight velocity distribution there.

to make the conclusion clearer.

### 2010-09-09 tex/hercules.tex
hercules: one more comment

The prospects to detect the Hercules feature are quite good on our
side of the Galaxy. The Hercules feature is especially strong in the
line-of-sight velocity distribution for Galactic longitudes
$250^{\circ} \lesssim l \lesssim 290^{\circ}$. This is because of the
fortunate coincidence that for those lines-of-sight we see velocities
in the direction along which the Hercules streams separates most from
the bulk of the velocity distribution (see
\figurename~\ref{fig:rphi2d}) and that at these azimuths the Hercules
stream is at the furthest distance from the rest of the velocity
distribution. We see hardly any effect of the bar on the line-of-sight
velocity distributions on the other side of the Galaxy ($90^{\circ}
\leq \phi \leq 270^{\circ}$). On that side we mostly see the
Galactocentric radial velocity in the line-of-sight, in which the
Hercules feature does not separate clearly from the bulk of the
stars. Even though upcoming surveys such as \apogee\ have the ability
to probe the other side of the Galaxy, for the purposes of detecting
the Hercules stream this is uninteresting.

>>>>

The prospects to detect the Hercules feature are quite good on our
side of the Galaxy. The Hercules feature is especially strong in the
line-of-sight velocity distribution for Galactic longitudes
$250^{\circ} \lesssim l \lesssim 290^{\circ}$. This is because of the
fortunate coincidence that for those lines-of-sight we see velocities
in the direction along which the Hercules streams separates most from
the bulk of the velocity distribution (see
\figurename~\ref{fig:rphi2d}) and that at these azimuths the Hercules
stream is at the furthest distance from the rest of the velocity
distribution. We see hardly any effect of the bar on the line-of-sight
velocity distributions on the other side of the Galaxy ($90^{\circ}
\leq \phi \leq 270^{\circ}$). On that side we mostly see the
Galactocentric radial velocity in the line-of-sight, in which the
Hercules feature does not separate clearly from the bulk of the
stars. Even though upcoming surveys such as \apogee\ have the ability
to probe the other side of the Galaxy, for the purposes of detecting
the Hercules stream this is uninteresting as it does not show up in
the line-of-sight velocity distribution there.
